A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 5_generalization.tex
Tim: nominal => preferred
'nominal size' is the size something is supposed to be on paper; that wouldn't work for a sentence like
'The evenly distributed scheme can be conceptualized as calculating the total discrepancy $ between the actual feature diameter $ and the total preferred width  w^*$'
make transition overlap into wrapfigure to save space

The following restrictions hold:
\begin{enumerate}
\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth,frame]{sources-method-transition-length-limit.pdf}
\caption{
Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
}
\label{transition_placement}
\end{figure}

@@

\paragraph{Inward distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w^* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $\omega(n,r)$, which defines the portion of the discrepancy to distribute to each bead.
%\paragraph{Inward distributed}
See \cref{formula_inward_distributed}.
For example, we can choose an $\omega$ which distributes the discrepancy over the innermost $N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
%Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.

>>>>

The following restrictions hold:
\begin{enumerate}
	\begin{minipage}{\columnwidth}
	\setlength\intextsep{0pt}
	\begin{wrapfigure}[4]{o}{.4\columnwidth} %\centering
	\includegraphics[width=.3\columnwidth,frame]{sources-method-transition-length-limit.pdf}
	%\caption{
	%%Transition ends (magenta and pink) shouldn't cross each other.
	%Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
	%The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
	%}
	\label{transition_placement}
	\end{wrapfigure}
	\item Transitions shouldn't overlap each other: \\ $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ \\ for each $n \in \mathbb{N}$ \\ (see \cref{transition_placement})
\end{minipage}
\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
\end{enumerate}

@@

\paragraph{Inward distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w^* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $\omega(n,r)$, which defines the portion of the discrepancy to distribute to each bead.
%\paragraph{Inward distributed}
See \cref{formula_inward_distributed}.
For example, we can choose an $\omega$ which distributes the discrepancy over the innermost $N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the preferred bead width $w^*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
%Moreover, the bead widths equal the preferred bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
